---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tailor

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/tailor)](https://CRAN.R-project.org/package=tailor)
[![R-CMD-check](https://github.com/tidymodels/tailor/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tidymodels/tailor/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/tidymodels/tailor/graph/badge.svg)](https://app.codecov.io/gh/tidymodels/tailor)
<!-- badges: end -->

Postprocessors refine predictions outputted from machine learning models to improve predictive performance or better satisfy distributional limitations. This package introduces 'tailor' objects, which compose iterative adjustments to model predictions. In addition to utilities to create new adjustments, the package provides a number of pre-written ones:

* For probability distributions: calibration
* For transformation of probabilities to hard class predictions: thresholds, equivocal zones
* For numeric distributions: calibration, range

Tailors are tightly integrated with the [tidymodels](https://tidymodels.org) framework. For greatest ease of use, situate tailors in model [workflows](https://workflows.tidymodels.org) with `add_tailor()`.

The package is under active development; please treat it as experimental and don't depend on the syntax staying the same.

## Installation

You can install the development version of tailor like so:

``` r
pak::pak("tidymodels/tailor")
```

## Example

```{r}
library(tailor)
```

The `two_class_example` dataset from modeldata gives the true value of an outcome variable `truth` as well as predicted probabilities (`Class1` and `Class2`). The hard class predictions, in `predicted`, are `"Class1"` if the probability assigned to `"Class1"` is above `.5`, and `"Class2"` otherwise.

```{r}
library(modeldata)
library(dplyr)

head(two_class_example)
```

The model predicts `"Class1"` more often than it does `"Class2"`.

```{r}
two_class_example %>% count(predicted)
```

If we wanted the model to predict `"Class2"` more often, we could increase the probability threshold assigned to `"Class1"` above which the hard class prediction will be `"Class1"`. In the tailor package, this adjustment is implemented in `adjust_probability_threshold()`, which can be situated in a tailor object.

```{r}
post_obj <-
  tailor() %>%
  adjust_probability_threshold(threshold = .9)

post_obj
```

tailors must be fitted before they can predict on new data. For adjustments like `adjust_probability_threshold()`, there's no training that actually happens at the `fit()` step besides recording the name and type of relevant variables. For other adjustments, like probability calibration with `adjust_probability_calibration()`, parameters are actually estimated at the `fit()` step and separate data should be used to train the postprocessor and evaluate its performance.

In this case, though, we can `fit()` on the whole dataset. The resulting object is still a tailor, but is now flagged as trained.

```{r}
post_res <- fit(
  post_obj,
  two_class_example,
  outcome = c(truth),
  estimate = c(predicted),
  probabilities = c(Class1, Class2)
)

post_res
```

When used with a model [workflow](https://workflows.tidymodels.org) via `add_tailor()`, the arguments to `fit()` a tailor will be set automatically (in addition to the data splitting needed for postprocessors that require training).

Now, when passed new data, the trained tailor will determine the outputted class based on whether the probability assigned to the level `"Class1"` is above `.9`, resulting in more predictions of `"Class2"` than before.

```{r}
predict(post_res, two_class_example) %>% count(predicted)
```

Tailors compose adjustments; when several `adjust_*()` functions are called iteratively, tailors will apply them in order at `fit()` and `predict()` time. 
